\chapter{Methodology}

%%what approach
To provide a sound answer to how hindsight experience replay performs on harder tasks in contrast to easier tasks, the obvious approach is a quantitative approach. 
%%how to collect data
In order to collect data, a simulation environment is built for tasks of different difficulties. The robotic arm is trained for those tasks with hindsight experience replay. The performance for the training period is measured. The data will show the performance on the tasks over time and characteristics like learning rate and consistency is shown through the data. 
%%what scientific method is used for this data -> comparison
Data between easier and harder tasks is evaluated and compared to show how hindsight experience replay performs on different tasks. 
%%hgg
In some cases, it is clear that hindsight experience replay fails for the harder tasks. Possible reasons for the lack of performance are presented. An alternative extension for hindsight experience replay, hindsight goal generation will be used in addition to show possible approaches on solving the tasks with her for harder tasks. Hindsight goal generation will also be used on the easier tasks to make them comparable.
%%valid, reliable, reproducable
Validity is obviously given, because the data measured is exactly the performance and learning rate of the robotic arm which is the measurement needed to evaluate the performance of hindsight experience replay.
Similar results can be reproduced when repeating the data collection. The results are not necessarily exactly the same when reproduced. This is due to the nature of reinforcement learning as there is some randomness in the Markovian decision process when choosing an action. The law of large numbers %TODO\cite{bib1}
 states that with rising amount of samples the results will converge towards the expected probability. In context of reinforcement learning, the training time to learn needed might vary slightly, but the end performance should converge towards the same value with rising training time.

   